Assessing the impacts of time to detection distribution assumptions on detection probability estimation

### 2016-09-14 Draft.tex
Shorten title
Add keyword

\title{Hierarchical model assessing the impacts of time to detection distribution assumptions on detection probability estimation}

@@

{\bf Keywords:} abundance; availability; N-mixture model; point counts; removal sampling; survival analysis; Markov chain Monte Carlo; Stan

>>>>

\title{Assessing the impacts of time to detection distribution assumptions on detection probability estimation}

@@

{\bf Keywords:} abundance; availability; N-mixture model; point counts; removal sampling; survival analysis; Markov chain Monte Carlo; Stan; hierarchical model
